Your Title Here

### 2025-05-15 latex/draft.tex
更新论文

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[style=authoryear, backend=biber]{biblatex} % 使用biblatex
\addbibresource{references.bib} % 确保你的.bib文件名称正确

@@

@@

@@

@@

\subsection{Countries}
The analysis of national contributions to drone logistics research reveals a clear hierarchy in drone logistics research contributions across countries, measured by publication volume, citation impact, and H-index. The ​​United States​​ leads in citation impact (13,612 citations) and H-index (56), despite ranking second in publication count (384 studies), underscoring its dominant role in high-impact research. ​​China​​ ranks first in publication volume (528 studies) but second in citations (8,437) and H-index (45), reflecting a large-scale output with relatively lower per-study impact compared to the U.S. ​​South Korea​​ holds third place across all metrics (138 publications, 4,493 citations, H-index 36), demonstrating balanced productivity and impact.

European nations like Germany and Italy (83 publications each) achieve identical H-indices (27), demonstrating comparable scholarly influence at a moderate output level. ​​Canada​​ (75 publications, H-index 23) and ​​Australia​​ (72 publications, H-index 24) exhibit efficient research ecosystems with mid-tier citation traction (2,898 and 1,915 citations, respectively). ​​India​​ and ​​Saudi Arabia​​, while emerging as active contributors (110 and 55 publications), show lower H-indices (21 and unlisted), indicating room for greater global impact.

\subsection{Institutions}
In this section, we turn to analyzing high-impact institutions in drone logistics research.​​ ​​Sejong University​​ emerges as a leading institution with ​​1,712 total citations​​ and an ​​H-index of 19​​, driven by interdisciplinary collaborations. While most of its top-cited works focus on ​​consumer behavior and technology adoption​​ in drone food delivery (e.g., perceived innovativeness (\cite{WOS:000478712400012}), risk perception (\cite{WOS:000495004400013}), and COVID-19 impacts (\cite{WOS:000605628800016}))—led by ​​Jinsoo Hwang​​’s aforementioned behavioral science studies—its most cited paper, "Routing in Flying Ad Hoc Networks: A Comprehensive Survey" (218 citations), represents a distinct technical domain.This survey systematically categorizes routing protocols for ​​Flying Ad Hoc Networks (FANETs)​​, analyzing their strengths/weaknesses against challenges like high mobility and topology instability. It evaluates protocols using mobility models and proposes a taxonomy to guide future FANET communication design (\cite{WOS:000538038400010})​​. The institution’s research portfolio underscores a balanced emphasis on ​​technical and ​​socioeconomic research, positioning it as a hub for drone logistics innovation. Auburn University​​ holds a notable position in drone logistics research with ​​1,062 total citations​​, though its influence is overwhelmingly driven by a single landmark study: "The flying sidekick traveling salesman problem" (920 citations) (\cite{WOS:000353871700006}). ​​Purdue University's research in drone logistics spans optimization frameworks​​—mathematical models like insertion heuristics that handle large-scale routing across hundreds of nodes (\cite{WOS:000460496000002})—and ​​real-world constraint modeling​​, which integrates operational hurdles such as battery limits (\cite{WOS:000532795300023}), No-Fly Zones (\cite{WOS:000474324300017}), and multi-trip payload fluctuations (\cite{WOS:000523602300006}). University of Maryland has ​​947 total citations​​. Its foundational work, "The vehicle routing problem with drones: several worst-case results" (\cite{WOS:000400384200003})  (325 citations), quantified the maximum time savings achievable via drones under varying speed ratios and fleet sizes. A follow-up study  (229 citations) by the same institution expanded the previous study by linking it to ​​Amdahl’s Law​​, emphasizing how drones enhance efficiency via ​​parallel task execution (\cite{WOS:000404719400004})​​. ​​York University (Canada) and University of Calgary's influence in drone logistics are heavily anchored by a single landmark study: "Vehicle Routing Problems for Drone Delivery" (\cite{WOS:000391480400007}). Authored by Dorling et al., this work established ​​energy-aware multitrip routing models​​, integrating linear payload-battery energy consumption into MILP formulations and simulated annealing heuristics. The University of Florida's impact in drone logistics is dominated by "UAV-Enabled Intelligent Transportation Systems for the Smart City: Applications and Challenges" (\cite{WOS:000398037700003}) (609 citations, ~74\% of total citations). This study ​​maps UAV applications and ​​key challenges for smart-city intelligent transportation systems. State University of New York​​ has advanced drone logistics with ​​798 citations, focusing on ​​multi-drone coordinated delivery​​ (\cite{WOS:000509790500020}) and ​​barrier analysis (\cite{WOS:000547773000001})​​.

The interplay between publication volume, H-index, and total citations reveals distinct institutional research profiles in drone logistics. ​​Sejong University​​ exemplifies balanced excellence, ranking ​​4th in output​​ (27 papers) but ​​1st in both H-index (19) and total citations (1,712)​​, underscoring its dual strength in behavioral studies (\cite{WOS:000478712400012}) and technical innovations (\cite{WOS:000538038400010}). In contrast, ​​Hong Kong Polytechnic University​​ leads in sheer output (42 papers) but trails in H-index (14) and total citations (absent from the top 10), reflecting a high-volume yet moderately cited portfolio. Chinese institutions like ​​Nanjing University of Aeronautics & Astronautics​​ (2nd in output, 33 papers) and ​​Beihang University​​ (3rd, 28 papers) prioritize quantity but lack representation in H-index and citation rankings. Nanyang Technological University​​ (6th in output, 22 papers; 3rd in H-index, 13) and ​​University of New South Wales Sydney​​ (3rd in H-index, 13) achieve higher per-paper impact through optimization frameworks​​ (\cite{WOS:000501349900060}) and ​​collaborative delivery models​​ (\cite{WOS:000467564700204}). Tsinghua University (8th in output, 20 papers; 8th in H-index, 10), Purdue University (9th in output, 19 papers; 8th in H-index, 10) and the University of Maryland (9th in output, 19 papers; 8th in H-index, 10) demonstrate moderate yet consistent influence across output and impact metrics.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[style=authoryear, backend=biber]{biblatex} % 使用biblatex
\addbibresource{references.bib} % 确保你的.bib文件名称正确
\usepackage{graphicx}
\usepackage{booktabs} % 专业表格宏包
\usepackage{array}    % 增强表格对齐
\usepackage{tabularx} % 可选：适应文本宽度
\usepackage{placeins} % 在导言区添加
\usepackage{ragged2e}  % 文本对齐优化

\usepackage{threeparttable} % 表格注释支持
\newcolumntype{Y}{>{\RaggedRight\arraybackslash}X} % 自适应左对齐列

\usepackage{multirow} % 合并单元格（用于处理并列排名）

\graphicspath{{images/}} % 指定图片路径

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\textwidth, keepaspectratio]{images/Figure_1}
  \caption{Number of publications per year}
  \label{fig:Figure}
\end{figure}

@@

\begin{table}[htbp]
  \centering
  \caption{High-frequency Keywords in Drone Logistics Research}
  \label{tab:keyword_frequency}
  \begin{tabular}{@{} l r @{}} % 左对齐关键词，右对齐频率
    \toprule
    \textbf{Keyword} & \textbf{Frequency} \\
    \midrule
    Drone & 347 \\
    Unmanned aerial vehicle & 316 \\
    Routing & 90 \\
    Logistics & 80 \\
    Drone delivery & 79 \\
    Path planning & 57 \\
    Last-mile delivery & 50 \\
    Optimization & 43 \\
    Vehicle routing & 39 \\
    Delivery & 31 \\
    Transportation & 31 \\
    Covid-19 & 30 \\
    Vehicle routing problem & 27 \\
    Humanitarian logistics & 25 \\
    Traveling salesman problem & 24 \\
    Urban air mobility & 24 \\
    Parcel delivery & 23 \\
    Energy consumption & 23 \\
    Trajectory & 23 \\
    Task analysis & 21 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \caption{Top Cited Authors in Drone Logistics Research}
  \label{tab:ranked_authors}
  \begin{tabular}{@{} c l r @{}} % 三列：居中排名，左对齐作者，右对齐引用次数
    \toprule
    \textbf{Rank} & \textbf{Author} & \textbf{Citations} \\
    \midrule
    1 & Hwang, J & 1434 \\
    2 & Murray, CC & 1235 \\
    3 & Chu, AG & 920 \\
    4 & Poikonen, S & 867 \\
    5 & Lee, S & 857 \\
    6 & Kim, JJ & 812 \\
    7 & Golden, B & 784 \\
    \multirow{4}{*}{8} & Dorling, K & 766 \\ % 合并排名单元格
                        & Heinrichs, J & 766 \\
                        & Messier, GG & 766 \\
                        & Magierowski, S & 766 \\
    \bottomrule
  \end{tabular}
\end{table}

\FloatBarrier % 后续内容不会越过此屏障

@@

\begin{table}[htbp]
  \centering
  \caption{Top Cited Articles in Drone Logistics Research (2010-2023)}
  \label{tab:top_articles}
  \begin{tabularx}{\textwidth}{@{} >{\centering\arraybackslash}p{1.5cm} X r @{}}
    \toprule
    \textbf{Rank} & \textbf{Article Title} & \textbf{Citations} \\
    \midrule
    1 & The flying sidekick traveling salesman problem: Optimization of drone-assisted parcel delivery & 920 \\
    2 & Vehicle Routing Problems for Drone Delivery & 766 \\
    3 & UAV-Enabled Intelligent Transportation Systems for the Smart City: Applications and Challenges & 609 \\
    4 & Digital Supply Chain: Literature review and a proposed framework for future research & 579 \\
    5 & Optimization Approaches for the Traveling Salesman Problem with Drone & 523 \\
    6 & On the min-cost Traveling Salesman Problem with Drone & 375 \\
    7 & From high-touch to high-tech: COVID-19 drives robotics adoption & 336 \\
    8 & The vehicle routing problem with drones: several worst-case results & 325 \\
    9 & Energy use and life cycle greenhouse gas emissions of drones for commercial package delivery & 316 \\
    10 & Vehicle routing problem with drones & 311 \\
    \bottomrule
  \end{tabularx}
\end{table}

\FloatBarrier % 后续内容不会越过此屏障

\subsection{Countries}
The analysis of national contributions to drone logistics research reveals a clear hierarchy in drone logistics research contributions across countries, measured by publication volume, citation impact, and H-index. The United States leads in citation impact (13,548 citations) and H-index (56), despite ranking second in publication count (383 studies), underscoring its dominant role in high-impact research. China ranks first in publication volume (528 studies) but second in citations (8,437) and H-index (45), reflecting a large-scale output with relatively lower per-study impact compared to the U.S. South Korea holds third place across all metrics (138 publications, 4,493 citations, H-index 36), demonstrating balanced productivity and impact.

European nations like Germany (82 studies) and Italy (83 studies) achieve identical H-indices (27), demonstrating comparable scholarly influence at a moderate output level. Canada (75 publications, H-index 23) and Australia (72 publications, H-index 24) exhibit efficient research ecosystems with mid-tier citation traction (2,898 and 1,915 citations, respectively). India, while emerging as an active contributor (109 publications), show lower H-indices (21), indicating room for greater global impact.

\begin{table}[htbp]
  \centering
  \caption{National Research Output Metrics in Drone Logistics}
  \label{tab:research_metrics}
  \begin{tabularx}{0.9\textwidth}{@{} >{\RaggedRight}p{3cm} r r r @{}}
    \toprule
    \textbf{Country} & \textbf{Publications} & \textbf{Total Citations} & \textbf{H-index} \\
    \midrule
    USA              & 383  & 13548 & 56 \\
    Peoples R China  & 528  & 8437  & 45 \\
    South Korea      & 138  & 4493  & 36 \\
    Germany          & 82   & 2604  & 27 \\
    Italy            & 83   & 2023  & 27 \\
    England          & 110  & 1977  & 26 \\
    Australia        & 72   & 1915  & 24 \\
    Canada           & 75   & 2898  & 23 \\
    India            & 109  & 1582  & 21 \\
    Spain            & 52   & 1388  & 19 \\
    \bottomrule
  \end{tabularx}
\end{table}

\subsection{Institutions}
In this section, we turn to analyzing high-impact institutions in drone logistics research. Sejong University emerges as a leading institution with 1,712 total citations and an H-index of 19, driven by interdisciplinary collaborations. While most of its top-cited works focus on consumer behavior and technology adoption in drone food delivery (e.g., perceived innovativeness (\cite{WOS:000478712400012}), risk perception (\cite{WOS:000495004400013}), and COVID-19 impacts (\cite{WOS:000605628800016}))—led by Jinsoo Hwang’s aforementioned behavioral science studies—its most cited paper, "Routing in Flying Ad Hoc Networks: A Comprehensive Survey" (218 citations), represents a distinct technical domain.This survey systematically categorizes routing protocols for Flying Ad Hoc Networks (FANETs), analyzing their strengths/weaknesses against challenges like high mobility and topology instability. It evaluates protocols using mobility models and proposes a taxonomy to guide future FANET communication design (\cite{WOS:000538038400010}). The institution’s research portfolio underscores a balanced emphasis on technical and socioeconomic research, positioning it as a hub for drone logistics innovation. Auburn University holds a notable position in drone logistics research with 1,062 total citations, though its influence is overwhelmingly driven by a single landmark study: "The flying sidekick traveling salesman problem" (920 citations) (\cite{WOS:000353871700006}). Purdue University's research in drone logistics spans optimization frameworks—mathematical models like insertion heuristics that handle large-scale routing across hundreds of nodes (\cite{WOS:000460496000002})—and real-world constraint modeling, which integrates operational hurdles such as battery limits (\cite{WOS:000532795300023}), No-Fly Zones (\cite{WOS:000474324300017}), and multi-trip payload fluctuations (\cite{WOS:000523602300006}). University of Maryland has 947 total citations. Its foundational work, "The vehicle routing problem with drones: several worst-case results" (\cite{WOS:000400384200003})  (325 citations), quantified the maximum time savings achievable via drones under varying speed ratios and fleet sizes. A follow-up study  (229 citations) by the same institution expanded the previous study by linking it to Amdahl’s Law, emphasizing how drones enhance efficiency via parallel task execution (\cite{WOS:000404719400004}). York University (Canada) and University of Calgary's influence in drone logistics are heavily anchored by a single landmark study: "Vehicle Routing Problems for Drone Delivery" (\cite{WOS:000391480400007}). Authored by Dorling et al., this work established energy-aware multitrip routing models, integrating linear payload-battery energy consumption into MILP formulations and simulated annealing heuristics. The University of Florida's impact in drone logistics is dominated by "UAV-Enabled Intelligent Transportation Systems for the Smart City: Applications and Challenges" (\cite{WOS:000398037700003}) (609 citations, ~74\% of total citations). This study maps UAV applications and key challenges for smart-city intelligent transportation systems. State University of New York has advanced drone logistics with 798 citations, focusing on multi-drone coordinated delivery (\cite{WOS:000509790500020}) and barrier analysis (\cite{WOS:000547773000001}).

The interplay between publication volume, H-index, and total citations reveals distinct institutional research profiles in drone logistics. Sejong University exemplifies balanced excellence, ranking 4th in output (27 papers) but 1st in both H-index (19) and total citations (1,712), underscoring its dual strength in behavioral studies (\cite{WOS:000478712400012}) and technical innovations (\cite{WOS:000538038400010}). In contrast, Hong Kong Polytechnic University leads in sheer output (42 papers) but trails in H-index (14) and total citations (absent from the top 10), reflecting a high-volume yet moderately cited portfolio. Chinese institutions like Nanjing University of Aeronautics \& Astronautics (2nd in output, 33 papers) and Beihang University (3rd, 28 papers) prioritize quantity but lack representation in H-index and citation rankings. Nanyang Technological University (6th in output, 22 papers; 3rd in H-index, 13) and University of New South Wales Sydney (3rd in H-index, 13) achieve higher per-paper impact through optimization frameworks (\cite{WOS:000501349900060}) and collaborative delivery models (\cite{WOS:000467564700204}). Tsinghua University (8th in output, 20 papers; 8th in H-index, 10), Purdue University (9th in output, 19 papers; 8th in H-index, 10) and the University of Maryland (9th in output, 19 papers; 8th in H-index, 10) demonstrate moderate yet consistent influence across output and impact metrics.

\subsection{Sources}
The distribution of publications and citation impact across journals reveals distinct patterns in drone logistics research. Drones leads in publication volume (98 papers) but has the lowest average citations (7.34) among top-output journals. Subsequent examination of highly cited articles in Drones suggests a focus on rapid dissemination of applied or technical studies (\cite{WOS:000682822500001, WOS:000682822500021}). SUSTAINABILITY (57 papers, 16.88 avg. citations) ranks second in publication volume, reflecting its role in hosting interdisciplinary studies on drone logistics' environmental and societal impacts (\cite{WOS:000531558100214, WOS:000428567100315}). IEEE TRANSACTIONS ON INTELLIGENT TRANSPORTATION SYSTEMS (57 papers, 28.40 avg. citations) matches SUSTAINABILITY in output but achieves higher citations, indicative of its focus on routing innovations (\cite{WOS:000658360600026}) and UAV integration into adaptive traffic systems (\cite{WOS:000684003100038}). TRANSPORTATION RESEARCH PART C-EMERGING TECHNOLOGIES (53 papers) achieves the highest average citations (79.15) in this category, reflecting its prominence in publishing high-impact applied optimization studies (\cite{WOS:000353871700006, WOS:000425566000035}). IEEE ACCESS (46 papers, 16.00 avg. citations) and APPLIED SCIENCES-BASEL (38 papers, 7.50 avg. citations) prioritize rapid dissemination of applied research, with IEEE ACCESS showing marginally higher citation influence due to its engineering-focused scope. TRANSPORTATION RESEARCH PART E-LOGISTICS AND TRANSPORTATION REVIEW (36 papers, 34.31 avg. citations) publishes strategic analyses of drone logistics' cost-efficiency and supply chain integration (\cite{WOS:000488423300001}). EUROPEAN JOURNAL OF OPERATIONAL RESEARCH (33 papers, 29.73 avg. citations) and COMPUTERS \& INDUSTRIAL ENGINEERING (31 papers, 29.55 avg. citations) demonstrate balanced output and citations, focusing on operational research (\cite{WOS:000742554100008}) and computational methods for UAV routing (\cite{WOS:000460496000002}). Drone logistics research exhibits a dichotomy between high-output, application-focused journals (e.g., Drones with 98 papers) and lower-output, high-impact journals (e.g., Transportation Research Part C with 79.15 avg. citations).

\subsection{Discipline}
The disciplinary focus of drone logistics research has expanded significantly post-2020, reflecting evolving technological and operational priorities. Engineering, Electrical \& Electronic remains dominant (63 pre-2020 → 299 post-2020), driven by advancements in UAV hardware, energy efficiency, and IoT integration. Transportation Science \& Technology (51 → 265) and Operations Research \& Management Science (56 → 255) show accelerated growth, emphasizing route optimization and hybrid truck-drone coordinated systems. Emerging disciplines post-2020 include Management (127) and Remote Sensing (103), highlighting a shift toward strategic logistics governance and geospatial applications. The rise of Computer Science, Artificial Intelligence (26 → 108) and Remote Sensing underscores the field’s pivot toward data-driven decision-making, such as AI-enhanced routing and dynamic fleet coordination (\cite{WOS:000742554100008}). This evolution reflects drone logistics' maturation from technical feasibility (pre-2020) to multidisciplinary scalability (post-2020), bridging engineering innovations with managerial and computational advancements.
